Identity Blockchain - Proof of Identity

### 2022-07-23 paper.tex
register solidity

\newpage
\section{Registering $\kid$}
Register $\kid$ on \pbc{} by calling $$register\kid(H(Nin), \kid^{-1}("register\kid"), proofNinOwnsKid).$$
\begin{enumerate}[leftmargin=0cm]
\item[] \underline{Pseudo-solidity code}

\hfill\begin{minipage}{\dimexpr\textwidth-20px}
\begin{lstlisting}[language=Solidity]
  mapping(uint256 => uint256) public ninKidUsed;
  mapping(uint256 => bool) public kidInvalid;

  function registerKid(
    uint256 hNin, // hNin = H(Nin)
    uint256 vKid, // vKid = KidPrivate("registerKid")
    bytes proofNinOwnsKid
  ) public {
    uint256 previousKey = ninKidUsed[hNin];
    if (previousKey == vKid) return; // already registered
    bool isOwner = zksnarkverify(VK, [hNin, vKid], proofNinOwnsKid); // VK = verification key
    if (isOwner && !kidInvalid[vKid]) {
      if (previousKey != 0) kidInvalid[previousKey] = true;
      ninKidUsed[hNin] = vKid;
    }
  }
\end{lstlisting}
\xdef\tpd{\the\prevdepth}
\end{minipage}

@@

\item[] \underline{Remarks}
\begin{itemize}
\item[i)] An entity that knows $\kid$, e.g. the CA who certified the corresponding eID, can know that the Person has registered $\kid$ on \pbc{}.
\item[ii)] Reasoning for the choice of arguments: if $H(Nin, \kid^{-1}("register\kid"))$ was used as an argument, then TODO. On the other hand, the choice of arguments $Nin$ and $\kid^{-1}("register\kid")$ would TODO.
\end{itemize}
\end{enumerate}

@@

\item[] \underline{Remarks}
\begin{itemize}
\item[i)] Reasoning behind the choice of arguments: TODO
\end{itemize}

@@

\newpage
\section{zkp code}
\begin{lstlisting}
//pseudo zokrates zk-SNARK
import "hashes/sha256/512bitPacked" as sha256packed
import "ecc/babyjubjubParams.code" as context
import "ecc/proofOfOwnership.code" as proofOfOwnership

>>>>

\newpage
\section{Registering identity key ($\khk$)}
Register $\kid$ on \pbc{} by calling $$register\kid(H(Nin), \kid^{-1}("register\kid"), proofNinOwnsKid).$$
\begin{enumerate}[leftmargin=0cm]
\item[] \underline{Pseudo-solidity code}

\hfill\begin{minipage}{\dimexpr\textwidth-20px}
\begin{lstlisting}[language=Solidity]
  mapping(uint => uint) public ninKidUsed;
	mapping(uint => uint) public ninKidKpUsed;
  mapping(uint => bool) public kidInvalid;

  function register(
    uint hNin, // hNin = H(Nin)
		uint hNinKid,
		uint hNinKidKp,
		bool invalidate, //true if someone stole your previous id
		uint[2] memory proofPointA,
		uint[2][2] memory proofPointsB,
		uint[2] memory proofPointC,
  ) public {
		//Setting public arguments
		uint[] memory inputValues = new uint[](3);
		inputValues[0]=hNin;
		inputValues[1]=hNinKid;
		inputValues[2]=hNinKidKp;

    require(verifyProof(
			proofPointA,
			proofPointsB,
			proofPointC,
			inputValues
		));

    uint previousHNinKid = ninKidUsed[hNin];
    if (previousHNinKid != hNinKid and invalidate == true) {
			//If they are different, we need to invalidate old Kid
			kidInvalid[previousHNinKid] = true;
		}
		require(!kidInvalid[hNinKid]);

		ninKidUsed[hNin] = hNinKid;

		ninKidKpUsed[hNinKid] = hNinKidKp;

  }

\end{lstlisting}
\xdef\tpd{\the\prevdepth}
\end{minipage}

@@

\item[] \underline{Remarks}
\begin{itemize}
\item[i)] An entity that knows $\kid$, e.g. the CA who certified the corresponding eID, can know that the Person has registered $\kid$ on \pbc{}.
\item[ii)] Reasoning for the choice of arguments: if $H(Nin, \kid^{-1}("register\kid"))$ was used as an argument, then if someone tried to register with two different ids, we couldn't tell if $Nin$ was already used. On the other hand, the choice of arguments $Nin$ and $\kid^{-1}("register\kid")$ would be almost the same as $hNin$ and $\kid^{-1}("register\kid")$, because you can brute force all the possible $Nin$s and find the corresponding $hNins$.
\end{itemize}
\end{enumerate}

@@

\item[] \underline{Remarks}
\begin{itemize}
\item[i)] Reasoning behind the choice of arguments:
We want to connect $Nin$ with $\khk$ in a unique, but untraceable way.
If we only used $Nin\kid\khk$ then if someone used multiple $\khk$s we wouldn't be able to prove the connection to $Nin$ (i.e. they could register a lot of $\khk$s).
Hashing connects arguments, and makes them opaque without the knowledge of arguments (which in this case include private keys), so the arguments are opaque without the knowledge of private keys.
\end{itemize}

@@

\newpage
\underline{Pseudo-circom code}
Statements we need to check:
\begin{itemize}
	\item Check first step (Register $\kid$) still valid

\end{itemize}

\begin{lstlisting}
//pseudo zokrates zk-SNARK
import "hashes/sha256/512bitPacked" as sha256packed
import "ecc/babyjubjubParams.code" as context
import "ecc/proofOfOwnership.code" as proofOfOwnership
